LDR: A 2nd-gen, National GeoLD System

### 2021-08-23 manuscript.tex
preparation for publication

\title{L4DR: A 2nd-gen, national GeoLD system}
\titlerunning{Loc-I for Disaster Recovery}

\author{
    Nicholas J. Car\inst{1}\orcidID{0000-0002-8742-7730} \and \\
    Irina Bastrakova\inst{2}\orcidID{0000-0002-4643-7289}
}

@@

\begin{abstract}
Increasingly, multiple sources of data are available for disaster recovery planning and emergency service scheduling. Data sharing systems may
have to simultaneously cover multiple diverse use cases (e.g. social, environmental and economic) and be transparent, verifiable and trusted. 
The 2020 Australian bushfire crisis and the global COVID-19 pandemic are examples of complex crisis events where lots of data sources are available.\\

In 2018 – 2020, Australia built several \textit{Linked Data} ``spines'' - themed collections of interoperable reference data that simplify data 
integration in particular domains. 
The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
Loc-I delivered Linked Data forms of its datasets and provided infrastructure for their use as a single system.\\

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
    \caption{An informal architecture diagram of the L4DR project's \textit{Linked Data} infrastructure}
    \label{fig:l4dr-arch}
\end{figure}

>>>>

\title{LDR: A 2nd-gen, National GeoLD System}
\titlerunning{Loc-I for Disaster Recovery}

\author{
    Nicholas J. Car\inst{1}\orcidID{0000-0002-8742-7730} \and \\
    Irina Bastrakova\inst{2}\orcidID{0000-0002-4643-7289}
    \thanks{Copyright ©2021 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
}

@@

\begin{abstract} 
The 2020 Australian bushfire crisis and the global COVID-19 pandemic are examples of complex crisis events where the use of data from multiple sources was sought. In 2018 – 2020, Australia built several \textit{Linked Data} ``spines'' - themed collections of interoperable reference data that simplify data 
integration from multiple sources in particular domains. 
The spatial data spine, Loc-I (Location Index), consists of 7 nationally-significant spatial datasets, such as the \textit{Australian Statistical Geographies System}. 
Loc-I delivered Linked Data forms of its datasets and provided infrastructure for their use as a single system.\\

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.5\linewidth]{images/l4dr-arch.png}
    \caption{An informal architecture diagram of the LDR project's \textit{Linked Data} infrastructure}
    \label{fig:l4dr-arch}
\end{figure}
